\section{C -- Iroha's Obsession}

\begin{frame}[fragile]{Problema}

Iroha is very particular about numbers. There are $K$ digits that she dislikes: $D_1, D_2, \ldots,
D_K$.

She is shopping, and now paying at the cashier. Her total is $N$ yen (the currency of Japan), thus
she has to hand at least $N$ yen to the cashier (and possibly receive the change).

However, as mentioned before, she is very particular about numbers. When she hands money to the
cashier, the decimal notation of the amount must not contain any digits that she dislikes. Under
this condition, she will hand the minimum amount of money.

Find the amount of money that she will hand to the cashier.

\end{frame}

\begin{frame}[fragile]{Entrada e saída}

\textbf{Constraints}

\begin{itemize}
    \item $1\leq N < 10000$
    \item $1\leq K < 10$
    \item $0\leq D_1 < D_2 < \ldots < D_K \leq 9$
    \item $\{D_1, D_2, \ldots, D_K\} \neq \{1, 2, 3, 4, 5, 6, 7, 8, 9\}$
\end{itemize}

\vspace{0.1in}

\textbf{Input}

Input is given from Standard Input in the following format:
\begin{atcoderio}{llll}
$N$ & $K$ \\
$D_1$ & $D_2$ & \ldots & $D_K$ \\
\end{atcoderio}

\textbf{Output}

Print the amount of money that Iroha will hand to the cashier.

\end{frame}

\begin{frame}[fragile]{Exemplo de entradas e saídas}

\begin{minipage}[t]{0.45\textwidth}
\textbf{Entrada}
\begin{verbatim}
1000 8
1 3 4 5 6 7 8 9


9999 1
0
\end{verbatim}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\textbf{Saída}
\begin{verbatim}
2000



9999
\end{verbatim}
\end{minipage}
\end{frame}

\begin{frame}[fragile]{Solução}

    \begin{itemize}
        \item Seja $D$ o menor dígito que Iroha gosta e $k$ o número de dígitos decimais de $N$

        \item O número $x = DD\ldots D$, formado por $k + 1$ dígitos $D$, é um número válido para
            Iroha e maior do que $N$

        \item Assim, é possível procurar, um a um, pelo menor número válido, pois ele será maior 
            ou igual a $N$ inferior a $10N$

        \item Cada número $y \in [N, 10N)$ pode ser verificado em $O(\log y)$

        \item Assim a solução de busca completa teria complexidade $O(N\log N)$
    \end{itemize}

\end{frame}

\begin{frame}[fragile]{Solução $O(N\log N)$}
    \inputsnippet{cpp}{1}{20}{codes/C.cpp}
\end{frame}

\begin{frame}[fragile]{Solução $O(N\log N)$}
    \inputsnippet{cpp}{21}{41}{codes/C.cpp}
\end{frame}
