\section{POJ 1195 -- Mobile Phones}

\begin{frame}[fragile]{Problema}

Suppose that the fourth generation mobile phone base stations in the Tampere area operate as 
follows. The area is divided into squares. The squares form an $S \times S$ matrix with the rows 
and columns numbered from $0$ to $S-1$. Each square contains a base station. The number of active 
mobile phones inside a square can change because a phone is moved from a square to another or a 
phone is switched on or off. At times, each base station reports the change in the number of 
active phones to the main base station along with the row and the column of the matrix. 

Write a program, which receives these reports and answers queries about the current total number 
of active mobile phones in any rectangle-shaped area. 

\end{frame}

\begin{frame}[fragile]{Entrada e saída}

\textbf{Input}

The input is read from standard input as integers and the answers to the queries are written to standard output as integers. The input is encoded as follows. Each input comes on a separate line, and consists of one instruction integer and a number of parameter integers according to the following table. 

\begin{tabularx}{0.95\textwidth}{llX}
    \toprule
    \textbf{Instruction} & \textbf{Parameters} & \textbf{Meaning} \\
    \midrule
    $0$ & $S$ & Initialize the matrix size to $S\times S$ containing all zeros. This instruction
        is given only once and it will be the first instruction \\
    \bottomrule
\end{tabularx}

\end{frame}

\begin{frame}[fragile]{Entrada e saída}

\begin{tabularx}{0.95\textwidth}{llX}
    \toprule
    \textbf{Instruction} & \textbf{Parameters} & \textbf{Meaning} \\
    \midrule
    $1$ & $X$ $Y$ $A$ & Add $A$ to the number of active phons in table square ($X, Y$). $A$ may
        be positve or negative.\\
    \midrule
    $2$ & $L$ $B$ $R$ $T$ & Query the current sum of numbers of active mobile phones in squares
        ($X, Y$), where $L\leq X\leq R, B\leq Y\leq T$ \\
    \midrule
    $3$ & & Terminate program. This instruction is given only once and it will be the last
        instruction. \\
    \bottomrule
\end{tabularx}

\end{frame}

\begin{frame}[fragile]{Entrada e saída}
The values will always be in range, so there is no need to check them. In particular, if $A$ is 
negative, it can be assumed that it will not reduce the square value below zero. The indexing 
starts at 0, e.g. for a table of size $4 \times 4$, we have $0\leq X\leq 3$ and $0\leq Y\leq 3$. 

\vspace{0.2in}

Table size: $1 \times 1 \leq S \times S \leq 1024 \times 1024$

Cell value $V$ at any time: $0 \leq V \leq 32767$

Update amount: $-32768 \leq A \leq 32767$

No of instructions in input: $3 \leq U \leq 60002$

Maximum number of phones in the whole table: $M = 2^{30}$

\end{frame}


\begin{frame}[fragile]{Entrada e saída}

\textbf{Output}

Your program should not answer anything to lines with an instruction other than 2. If the instruction is 2, then your program is expected to answer the query by writing the answer as a single line containing a single integer to standard output.

\end{frame}


\begin{frame}[fragile]{Exemplo de entradas e saídas}

\begin{minipage}[t]{0.6\textwidth}
\textbf{Sample Input}
\begin{verbatim}
0 4
1 1 2 3
2 0 0 2 2 
1 1 1 2
1 1 2 -1
2 1 1 2 3 
3
\end{verbatim}
\end{minipage}
\begin{minipage}[t]{0.35\textwidth}
\textbf{Sample Output}
\begin{verbatim}
3
4
\end{verbatim}
\end{minipage}

\end{frame}

\begin{frame}[fragile]{Solução}

    \begin{itemize}
        \item Este problema pode ser resolvido diretamente através da implementação de uma
            árvore de Fenwick bidimensional

        \item Deve-se tomar alguns cuidados, porque o juiz roda em servidores antigos e
            os compiladores não são os mais recentes disponíveis

        \item Evite qualquer elemento que foi introduzido na linguagem C++ após a versão 98

        \item Evite os contêiners da STL

        \item Os índices usados começam em zero, e isto deve ser refletido na implementação
        
        \item O cabeçalho \code{c}{bits/stdc++.h} não está disponível

   \end{itemize}

\end{frame}

\begin{frame}[fragile]{Solução com complexidade $O(T(N + K)\log(N + K))$}
    \inputsnippet{cpp}{1}{21}{codes/1195.cpp}
\end{frame}

\begin{frame}[fragile]{Solução com complexidade $O(T(N + K)\log(N + K))$}
    \inputsnippet{cpp}{23}{43}{codes/1195.cpp}
\end{frame}

\begin{frame}[fragile]{Solução com complexidade $O(T(N + K)\log(N + K))$}
    \inputsnippet{cpp}{44}{62}{codes/1195.cpp}
\end{frame}

\begin{frame}[fragile]{Solução com complexidade $O(T(N + K)\log(N + K))$}
    \inputsnippet{cpp}{63}{83}{codes/1195.cpp}
\end{frame}
