\section{Codeforces Round \#470 (rated, Div. 2, based on VK Cup 2018 (Round 1)}

\begin{frame}[fragile]{Problema}

Bob is a farmer. He has a large pasture with many sheep. Recently, he has lost some of them due to wolf attacks. He thus decided to place some shepherd dogs in such a way that all his sheep are protected.

The pasture is a rectangle consisting of $R\times C$ cells. Each cell is either empty, contains a sheep, a wolf or a dog. Sheep and dogs always stay in place, but wolves can roam freely around the pasture, by repeatedly moving to the left, right, up or down to a neighboring cell. When a wolf enters a cell with a sheep, it consumes it. However, no wolf can enter a cell with a dog.

Initially there are no dogs. Place dogs onto the pasture in such a way that no wolf can reach any sheep, or determine that it is impossible. Note that since you have many dogs, you do not need to minimize their number.

\end{frame}

\begin{frame}[fragile]{Entrada e saída}

\textbf{Input}

First line contains two integers $R$ $(1\leq R\leq 500)$ and $C$ $(1\leq C\leq 500)$, denoting the 
number of rows and the numbers of columns respectively.

Each of the following $R$ lines is a string consisting of exactly $C$ characters, representing one 
row of the pasture. Here, '\texttt{S}' means a sheep, '\texttt{W}' a wolf and '\texttt{.}' an empty cell.
\end{frame}

\begin{frame}[fragile]{Entrada e saída}
\textbf{Output}

If it is impossible to protect all sheep, output a single line with the word "\texttt{No}".

Otherwise, output a line with the word "\texttt{Yes}". Then print $R$ lines, representing the 
pasture after placing dogs. Again, '\texttt{S}' means a sheep, '\texttt{W}' a wolf, '\texttt{D}' is 
a dog and '\texttt{.}' an empty space. You are not allowed to move, remove or add a sheep or a wolf.

If there are multiple solutions, you may print any of them. You don't have to minimize the number of dogs.

\end{frame}

\begin{frame}[fragile]{Exemplo de entradas e saídas}

\begin{minipage}[t]{0.5\textwidth}
\textbf{Sample Input}
\begin{verbatim}
6 6
..S...
..S.W.
.S....
..W...
...W..
......

1 2
SW
\end{verbatim}
\end{minipage}
\begin{minipage}[t]{0.45\textwidth}
\textbf{Sample Output}
\begin{verbatim}
Yes
..SD..
..SDW.
.SD...
.DW...
DD.W..
......

No
\end{verbatim}
\end{minipage}
\end{frame}

\begin{frame}[fragile]{Solução com complexidade $O(RC)$}

    \begin{itemize}
        \item O problema pode ser modelado como um grafo

        \item Os vértices são as células da malha, de cada vértice partem até quatro arestas,
            para cada um dos vizinhos posicionados nas direções cardeais, se existirem

        \item A travessia adequada é a BFS, uma vez que é necessário avaliar apenas os vizinhos
            diretos de um nó

        \item O problema não terá solução de uma ovelha tiver como um vizinho um lobo

        \item Caso contrário, basta posicionar um cachorro nos vizinhos vazios de uma ovelha

        \item De fato, como não é necessário minimizar o número de cachorros, basta colocar
            cachorros em todas as células vazias
   \end{itemize}

\end{frame}

\begin{frame}[fragile]{Solução AC com complexidade $O(RC)$}
    \inputsnippet{cpp}{1}{21}{948A.cpp}
\end{frame}

\begin{frame}[fragile]{Solução AC com complexidade $O(RC)$}
    \inputsnippet{cpp}{23}{43}{948A.cpp}
\end{frame}

\begin{frame}[fragile]{Solução AC com complexidade $O(RC)$}
    \inputsnippet{cpp}{44}{64}{948A.cpp}
\end{frame}
