%\section{Codeforces Round \#251 (Div. 2) -- Problem D: Devu and his Brother}

\begin{frame}[fragile]{Problema}

Devu and his brother love each other a lot. As they are super geeks, they only like to play with 
arrays. They are given two arrays $a$ and $b$ by their father. The array $a$ is given to Devu and 
$b$ to his brother.

As Devu is really a naughty kid, he wants the minimum value of his array $a$ should be at least as 
much as the maximum value of his brother's array $b$.

Now you have to help Devu in achieving this condition. You can perform multiple operations on the 
arrays. In a single operation, you are allowed to decrease or increase any element of any of the 
arrays by 1. Note that you are allowed to apply the operation on any index of the array multiple 
times.

You need to find minimum number of operations required to satisfy Devu's condition so that the 
brothers can play peacefully without fighting.

\end{frame}

\begin{frame}[fragile]{Entrada e saída}

\textbf{Input}

The first line contains two space-separated integers $n$, $m$ $(1\leq n, m\leq 10^5)$. The second 
line will contain $n$ space-separated integers representing content of the array $a$ 
$(1\leq a_i\leq 10^9)$. The third line will contain $m$ space-separated integers representing 
content of the array $b$ $(1\leq b_i\leq 10^9)$.

\vspace{0.2in}

\textbf{Output}

You need to output a single integer representing the minimum number of operations needed to satisfy Devu's condition.

\end{frame}

\begin{frame}[fragile]{Exemplo de entradas e saídas}

\begin{minipage}[t]{0.5\textwidth}
\textbf{Sample Input}
\begin{verbatim}
2 2
2 3
3 5

3 2
1 2 3
3 4

3 2
4 5 6
1 2
\end{verbatim}
\end{minipage}
\begin{minipage}[t]{0.45\textwidth}
\textbf{Sample Output}
\begin{verbatim}
3



4



0
\end{verbatim}
\end{minipage}
\end{frame}

\begin{frame}[fragile]{Solução com complexidade $O(N\log N)$}

    \begin{itemize}
        \item Seja $f(x) = \sum_i \alpha(a_i, x)$, onde $\alpha(a_i, x) = x - a_i$, se $a_i < x$,
            e $\alpha(a_i, x) = 0$, caso contrário

        \item De forma semelhante, seja $g(x) = \sum_j \beta(b_j, x)$, onde 
            $\beta(b_j, x) = b_j - x$, se $b_j > x$, e $\beta(b_j, x) = 0$, caso contrário

        \item Observe que as funções $f(x)$ e $g(x)$ representam os custos para tornar $x$ uma
            cota inferior ou superior dos vetores $a$ e $b$, respectivamente

        \item Assim, o problema consiste em determinar o mínimo da função $h(x) = f(x) + g(x)$

        \item Observe que $h'(x) = \mu(a, x) - \rho(b, x)$, onde $\mu(c, x)$ é o número de 
            elementos do vetor $a$ menores do que $x$ e $\rho(b, x)$ é o número de elementos do
            vetor $b$ maiores do que $x$

        \item Como a função $\mu(a, x)$ é não-decrescente e a função $\rho(c, x)$ é não-crescente, 
            a $h'(x)$ é não-decrescente

        \item Isto significa que $h''(x) \geq 0$, ou seja, $h(x)$ é convexa (unimodal),
            de modo que seu mínimo pode ser obtido através de uma busca ternária
   \end{itemize}

\end{frame}

\begin{frame}[fragile]{Solução AC com complexidade $O(N\log N)$}
    \inputsnippet{cpp}{1}{19}{codes/439D.cpp}
\end{frame}

\begin{frame}[fragile]{Solução AC com complexidade $O(N\log N)$}
    \inputsnippet{cpp}{21}{40}{codes/439D.cpp}
\end{frame}

\begin{frame}[fragile]{Solução AC com complexidade $O(N\log N)$}
    \inputsnippet{cpp}{42}{62}{codes/439D.cpp}
\end{frame}
