\section{Codeforces Alpha Round \#20 (Codeforces format) -- Problem C: Dijkstra?}

\begin{frame}[fragile]{Problema}

You are given a weighted undirected graph. The vertices are enumerated from 1 to $n$. Your task is to find the shortest path between the vertex 1 and the vertex $n$.

\end{frame}

\begin{frame}[fragile]{Entrada e saída}

\textbf{Input}

The first line contains two integers $n$ and $m$ $(2\leq n\leq 10^5, 0\leq m\leq 10^5)$, where 
$n$ is the number of vertices and $m$ is the number of edges. Following m lines contain one edge 
each in form $a_i, b_i$ and $w_i$ $(1\leq a_i, b_i\leq n, 1\leq w_i\leq 10^6)$, where 
$a_i, b_i$ are edge endpoints and $w_i$ is the length of the edge.

It is possible that the graph has loops and multiple edges between pair of vertices.

\textbf{Output}

Write the only integer -1 in case of no path. Write the shortest path in opposite case. If there are many solutions, print any of them.

\end{frame}

\begin{frame}[fragile]{Exemplo de entradas e saídas}

\begin{minipage}[t]{0.5\textwidth}
\textbf{Sample Input}
\begin{verbatim}
5 6
1 2 2
2 5 5
2 3 4
1 4 1
4 3 3
3 5 1

5 6
1 2 2
2 5 5
2 3 4
1 4 1
4 3 3
3 5 1
\end{verbatim}
\end{minipage}
\begin{minipage}[t]{0.45\textwidth}
\textbf{Sample Output}
\begin{verbatim}
1 4 3 5 







1 4 3 5 
\end{verbatim}
\end{minipage}
\end{frame}

\begin{frame}[fragile]{Solução com complexidade $O(N + M\log M)$}

    \begin{itemize}
        \item O nome do problema efetivamente aponta a solução

        \item O algoritmo de Dijkstra pode ser utilizado tanto para computar o caminho
            mínimo quanto para reconstruir este caminho

        \item É preciso atentar ao fato de que a distância mínima pode exceder a capacidade
            de um inteiro, sendo necessário o uso de variáveis do tipo \code{c}{long long}

        \item Também é preciso ter cuidado com o tratamento dos casos onde não há caminho de
            1 a $N$

        \item Como o número de vértices é grande, o algoritmo de Bellman-Ford leva ao TLE
   \end{itemize}

\end{frame}

\begin{frame}[fragile]{Solução AC com complexidade $O(N\log N)$}
    \inputsnippet{cpp}{1}{21}{20C.cpp}
\end{frame}

\begin{frame}[fragile]{Solução AC com complexidade $O(N\log N)$}
    \inputsnippet{cpp}{23}{43}{20C.cpp}
\end{frame}

\begin{frame}[fragile]{Solução AC com complexidade $O(N\log N)$}
    \inputsnippet{cpp}{45}{65}{20C.cpp}
\end{frame}

\begin{frame}[fragile]{Solução AC com complexidade $O(N\log N)$}
    \inputsnippet{cpp}{66}{83}{20C.cpp}
\end{frame}

\begin{frame}[fragile]{Solução AC com complexidade $O(N\log N)$}
    \inputsnippet{cpp}{84}{104}{20C.cpp}
\end{frame}
