\begin{frame}[fragile]{AtCoder Beginner Contest 123B -- Five Dishes}

The restaurant AtCoder serves the following five dishes:

\begin{itemize}
    \item ABC Don (rice bowl): takes $A$ minutes to serve.
    \item ARC Curry: takes $B$ minutes to serve.
    \item AGC Pasta: takes $C$ minutes to serve.
    \item APC Ramen: takes $D$ minutes to serve.
    \item ATC Hanbagu (hamburger patty): takes $E$ minutes to serve.
\end{itemize}

Here, the time to serve a dish is the time between when an order is placed and when the dish is delivered.
\end{frame}

\begin{frame}[fragile]{AtCoder Beginner Contest 123B -- Five Dishes}
This restaurant has the following rules on orders:

\begin{itemize}
    \item An order can only be placed at a time that is a multiple of $10$ (time $0, 10, 20, \ldots$).
    \item Only one dish can be ordered at a time.
    \item No new order can be placed when an order is already placed and the dish is still not delivered, but a new order can be placed at the exact time when the dish is delivered.
\end{itemize}

E869120 arrives at this restaurant at time $0$. He will order all five dishes. Find the earliest possible time for the last dish to be delivered.

Here, he can order the dishes in any order he likes, and he can place an order already at time $0$.
\end{frame}

\begin{frame}[fragile]{Entrada e saída}

\textbf{Constraints}

\begin{itemize}
    \item $A,B,C,D$ and $E$ are integers between $1$ and $123$ (inclusive).
\end{itemize}

\vspace{0.1in}

\textbf{Input}

Input is given from Standard Input in the following format:
\begin{atcoderio}{lll}
$A$ \\
$B$ \\
$C$ \\
$D$ \\
$E$ \\
\end{atcoderio}

\textbf{Output}

Print the earliest possible time for the last dish to be delivered, as an integer.

\end{frame}

\begin{frame}[fragile]{Exemplos de entradas e saídas}

\begin{minipage}[t]{0.45\textwidth}
\textbf{Entrada}
\begin{verbatim}
29
20
7
35
120


101
86
119
108
57
\end{verbatim}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\textbf{Saída}
\begin{verbatim}
215






481
\end{verbatim}
\end{minipage}
\end{frame}


\begin{frame}[fragile]{Solução com complexidade $O(1)$}

    \begin{itemize}
        \item A solução consiste em determinar uma permutação dos pratos A, B, C, D e E que 
            minimize o tempo para serví-los

        \item Se não houvesse a restrição de que os pratos só podem ser pedidos em instantes de
            tempo que são múltiplos de 10, qualquer permutação levaria ao mesmo resultado

        \item Há $5! = 120$ permutações possíveis, as quais podem ser geradas por meio da 
            função \code{cpp}{next_permutation()}

        \item O $i$-ésimo prato requer $t_i$ minutos para ser servido após ser pedido e, exceto
            pelo último, é preciso esperar o próximo múltiplo de 10 para ser pedido

        \item Uma forma de tratar esta espera é substituir $t_i$ pelo menor múltiplo de 10 maior
            ou igual a $t_i$ para todos os pratos, exceto o último
    \end{itemize}

\end{frame}

\begin{frame}[fragile]{Solução com complexidade $O(1)$}
    \inputsnippet{cpp}{7}{22}{codes/B123B.cpp}
\end{frame}
